Time stability in human interaction networks

### 2015-06-06 paper.tex
arrumado agradecimentos

\begin{acknowledgments}
	Financial support was obtained from CNPq (140860/2013-4,
	project 870336/1997-5), United Nations Development Program (PNUD/ONU, contract: 2013/000566; project BRA/12/018) and FAPESP. The authors are grateful to the American Jewish Committee for maintaining an online copy of the Adorno book used on the epigraph~\cite{adorno}, to GMANE creators and maintainers, and to the communities of the email lists and other groups used in the analysis, and to the Brazilian Presidency for keeping Participa.br code and data open. We are also grateful to developers and users of Python scientific tools.
\end{acknowledgments}

>>>>

\begin{acknowledgments}
	Financial support was obtained from CNPq (140860/2013-4,
	project 870336/1997-5), United Nations Development Program (contract: 2013/000566; project BRA/12/018) and FAPESP. 
	The authors are grateful to the American Jewish Committee for maintaining an online copy of the Adorno book used on the epigraph~\cite{adorno}, to GMANE creators and maintainers, and to the communities of the email lists and other groups used in the analysis, and to the Brazilian Presidency of the Republic for keeping Participa.br code and data open.
	We are also grateful to developers and users of Python scientific tools.
\end{acknowledgments}
